---
title: "Caterina Almazan_Community Contribution Project"
format: html
editor: visual
---

## Plotscaper

Plotscaper is an R package designed for creating interactive figures for data exploration. All plots in `plotscaper` are automatically linked and support several kinds of interactive features: including selection, zooming, panning, and parameter manipulation. The figures can be interacted with either manually, using a mouse and a keyboard, or by running code from inside an active R session.

```{r}
install.packages("plotscaper")
```

## Ozone & Environmental data demo

```{r}
library(plotscaper)

names(airquality) <- c("ozone", "solar radiation", "wind", 
                       "temperature", "month", "day")

create_schema(airquality) |>
  add_scatterplot(c("solar radiation", "ozone")) |>
  add_barplot(c("day", "ozone"), list(reducer = "max")) |>
  add_histogram(c("wind")) |>
  add_pcoords(names(airquality)[1:4]) |>
  render()
```

## Sacramento demo

```{r}
install.packages("caret")
```

```{r}
library(plotscaper)
library(caret)
library(dplyr)

data("Sacramento")

dplyr::glimpse(Sacramento)

```

```{r}
create_schema(Sacramento) |>
  add_scatterplot(c("longitude", "latitude"), list(ratio = 1)) |>
  add_barplot(c("city")) |>
  add_fluctplot(c("beds", "baths")) |>
  add_histogram(c("sqft")) |>
  render()
  #select_cases(1:100)
```

```{r}
schema <- create_schema(Sacramento) |>
  add_scatterplot(c("longitude", "latitude"), list(ratio = 1)) |>
  add_barplot(c("city")) |>
  add_fluctplot(c("beds", "baths")) |>
  add_histogram(c("sqft")) |>
  select_cases(1:100)

scene <- schema |> render()

scene |> add_scatterplot(c("sqft", "price"))
```
